### 2017-12-10 journal/anatomy.tex
Added IEEE Journal formatting

\noindent\textbf{Detecting flakiness.}  Modern build systems provide
mechanisms to reveal test flakiness. The typical approach is to
iteratively re-execute the test suite marking as flaky those tests
that produce both pass and failing outputs.  Considering the
Maven\Fix{is this maven or maven's surefire
  plugin~\cite{maven-surefire-plugin}?}  build system, the process
starts with the developer determining a bound N for the number of
re-executions of the test suite.  Only tests that fail in one given
iteration are scheduled for re-execution in the next iteration.  At
the end of the process, a test is considered passing if it passes in
the first iteration, a test is considered failing if it fails in all
iterations, and it is considered flaky if it fails in all iterations
but the last it executed.  The process terminates when all tests
eventually pass or when the bound N is reached.  Note that every
iteration runs a subset of the tests from the previous iteration so
execution cost is lower compared to executing the entire test suite N
times.

\Fix{Ideally, one would like to eliminate \pef{}s and avoid the need
  for re-executing the test suite multiple times.}

>>>>

\subsection{Detecting flakiness.}
\label{sec:detect-flakiness-build}

A popular approach to detect test flakiness is to iteratively
re-execute (parts of) the test suite multiple times marking as flaky
those tests that produce both pass and failing outputs.  We refer to
this process as IRE (for Iterative RE-execution).

Considering the Maven\Fix{is this maven or maven's surefire
  plugin~\cite{maven-surefire-plugin}?} build system, the process
starts with the developer determining a bound N for the number of
re-executions of the test suite.  Only tests that fail in one given
iteration are scheduled for re-execution in the next iteration.  At
the end of the process, a test is considered passing if it passes in
the first iteration, a test is considered failing if it fails in all
iterations, and it is considered flaky if it fails in all iterations
but the last it executed.  The process terminates when all tests
eventually pass or when the bound N is reached.  Note that every
iteration runs a subset of the tests from the previous iteration so,
assuming most tests will pass in the first iterations, execution cost
is much lower compared to executing the entire test suite N times.
However, note also that this method can particularly miss flaky tests
for the following reasons: \Fix{elaborate: (1) passing tests can fail
  in subsequent iterations and (2) ignoring tests may prevent
  manifestations of read-write conflicts.}

\Fix{explain other method...}

%%  LocalWords:  iteratively

### 2017-12-10 journal/related.tex
Added IEEE Journal formatting

\section{Related Work}
\label{sec:related}
We discuss most related work in the following.
%% Researchers and practitioners have been shedding light to the demand
%% of techniques for optimizing test execution.

%% For instance, a recent paper from the automotive industry reported
%% that test suites can take days to run~\cite{artl-etal-icst2015}.
%% There are different aspects to consider when dealing with the
%% challenge of reducing test cost.

%ekstazi-web,
Regression testing research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012,soetens-etal-2016}.  Most of these
techniques are unsound (\ie{}, they do not guarantee that
fault-revealing tests will be considered for testing).  The test
selection technique
Ekstazi~\cite{gligoric-etal-issta2015,celik-etal-fse2017} is an
example of a sound regression testing technique. It conservatively
computes which tests have been impacted by file changes.  A test is
discarded for execution if it does not depend on any changed file
dynamically reachable from execution.\Comment{ Curiously Ekstazi's
  evaluation discovered subjects with parallelism enabled by
  default.}\Comment{ \c{C}elik~\etal{}~\cite{} recently extended
  Ekstazi to track files accessed outside JVM boundaries.} Important
to note that regression testing techniques, including test selection,
is complementary to test suite parallelization.

%\Luis{maybe we should create another division for test acceleration}

@@

%% \textit{Usage of massively parallel hardware:}
%\textit{Hardware level massive parallelization:}

@@

%% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
%% language.
%% Recent work proposed a compiler-assisted approach to make programs
%% compatible with the relying programming-model used by
%% GPUs to parallelize tests~\cite{}.
%% \Jbc{...Justify they are out of scope for our subjects...}.

%% \Mar{Luis, por favor, revise$\rightarrow$}

@@

\Comment{
\Fix{Please:
  (i) consider categorizing related work in sections  
  (ii) list papers that need to be discussed
  (iii) discuss papers that use multi-execution (SIMD cpus like GPUs)
  to speedup testing
  }
}
\Comment{
Similar approach to regression test selection has been recently
applied in the context of the GCC~\cite{gcc} configurable
system~\cite{souto-damorim-jss}.
O Trabalho de Hilton ext al~\cite{hilton-etal-ase2016}, embora tenha
como objetivo entender o uso de CI, mostra que existe uma demanda em
acelerar o build e execucao de testes em servidores de integracao
    continua
}

>>>>

\section{Related Work}
\label{sec:related}

Regression testing research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012,soetens-etal-2016}.  Most of these
techniques are unsound (\ie{}, they do not guarantee that
fault-revealing tests will be considered for testing).  The test
selection technique
Ekstazi~\cite{gligoric-etal-issta2015,celik-etal-fse2017} is an
example of a sound regression testing technique. It conservatively
computes which tests have been impacted by file changes.  A test is
discarded for execution if it does not depend on any changed file
dynamically reachable from execution.\Comment{ Curiously Ekstazi's
  evaluation discovered subjects with parallelism enabled by
  default.}\Comment{ \c{C}elik~\etal{}~\cite{} recently extended
  Ekstazi to track files accessed outside JVM boundaries.} Important
to note that regression testing techniques, including test selection,
is complementary to test suite parallelization.

@@

@@

@@
